---
title: "RFP heatmap report (4 scenarios)"
author: "Hilaire et al. (2022)"
output:
  word_document:
    toc: yes
    toc_depth: '2'
    fig_width: 12
    fig_height: 9
---

```{r user_section, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
u_dr       <- 0.05
u_horizon  <- 2050
u_scenario <- "Net Zero 2050"
u_sum_type <- "TOTAL"
u_models   <- c("GCAM5.3_NGFS", "MESSAGEix-GLOBIOM 1.1", "REMIND-MAgPIE 2.1-4.2") 
u_sectors_energysupply  <- rev(c("Energy Supply|Production|Oil", "Energy Supply|Production|Gas", 
                                 "Energy Supply|Production|Coal",  
                                 "Energy Supply|Production|Biomass"))


u_sectors_electricutilities  <- rev(c("Energy Supply|Electric Utilities|Coal", 
                                 "Energy Supply|Electric Utilities|Gas", "Energy Supply|Electric Utilities|Nuclear", 
                                 "Energy Supply|Electric Utilities|Biomass", 
                                 "Energy Supply|Electric Utilities|Non-Biomass Renewables", 
                                 "Energy Supply|Electric Utilities|Non-Biomass Renewables|Solar PV", 
                                 "Energy Supply|Electric Utilities|Non-Biomass Renewables|Wind", 
                                 "Energy Supply|Electric Utilities|Non-Biomass Renewables|Hydro"))
                                 
u_sectors_liquidsplants  <- rev(c("Energy Supply|Refineries|Oil", "Energy Supply|Fischer-Tropsch Process|Biomass"))

u_sectors_h2plants  <- rev(c("Energy Supply|Hydrogen Plants|Coal", "Energy Supply|Hydrogen Plants|Gas", 
                                 "Energy Supply|Hydrogen Plants|Biomass", "Energy Supply|Hydrogen Plants|Electricity"))

u_sectors_energydemand  <- rev(c("End-Use|Residential and Commercial", "End-Use|Industry", 
                                 "End-Use|Industry|Cement", "End-Use|Industry|Chemicals", 
                                 "End-Use|Industry|Steel", "End-Use|Industry|Other", "End-Use|Transportation"))


```


```{r init, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
# Load libraries
library(tidyverse)
library(ggpubr)
library(PTXQC)

# Load rfp functions
source("../functions/rfp.R")

# Load plotting functions
source("../functions/plotting_functions.R")

# Load computed RFPs
load("../data/data_rfp_step2.RData")
```

This report is generated automatically from the R-Markdown file rfp_report_heatmap_multiscenario_docx.Rmd.

G is for GCAM, MG for MESSAGEix-GLOBIOM, RM for REMIND-MAgPIE

# Scenario: Net Zero 2050
## World
```{r}
v_region <- "World"
```

### Primary energy production
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_energysupply, u_models, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_electricutilities, u_models, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_liquidsplants, u_models, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_h2plants, u_models, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region == v_region, scenario == u_scenario), u_sectors_energydemand, u_models, SUM=u_sum_type)

```


## China
```{r}
v_regionall <- c("GCAM5.3_NGFS|China", 
              "MESSAGEix-GLOBIOM 1.1|R11_CPA", 
              "REMIND-MAgPIE 2.1-4.2|CHA")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


## EU
```{r}
v_regionall <- c("GCAM5.3_NGFS|EU-12", 
              "MESSAGEix-GLOBIOM 1.1|R11_WEU", 
              "REMIND-MAgPIE 2.1-4.2|EUR")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


## India
```{r}
v_regionall <- c("GCAM5.3_NGFS|India", 
              "MESSAGEix-GLOBIOM 1.1|R11_SAS", 
              "REMIND-MAgPIE 2.1-4.2|IND")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


## USA
```{r}
v_regionall <- c("GCAM5.3_NGFS|USA", 
              "MESSAGEix-GLOBIOM 1.1|R11_NAM", 
              "REMIND-MAgPIE 2.1-4.2|USA")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```



# Scenario: Divergent Net Zero
```{r}
u_scenario <- "Divergent Net Zero"
```
## World
```{r}
v_region <- "World"
```

### Primary energy production
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_energysupply, u_models, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_electricutilities, u_models, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_liquidsplants, u_models, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_h2plants, u_models, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region == v_region, scenario == u_scenario), u_sectors_energydemand, u_models, SUM=u_sum_type)

```


## China
```{r}
v_regionall <- c("GCAM5.3_NGFS|China", 
              "MESSAGEix-GLOBIOM 1.1|R11_CPA", 
              "REMIND-MAgPIE 2.1-4.2|CHA")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


## EU
```{r}
v_regionall <- c("GCAM5.3_NGFS|EU-12", 
              "MESSAGEix-GLOBIOM 1.1|R11_WEU", 
              "REMIND-MAgPIE 2.1-4.2|EUR")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


## India
```{r}
v_regionall <- c("GCAM5.3_NGFS|India", 
              "MESSAGEix-GLOBIOM 1.1|R11_SAS", 
              "REMIND-MAgPIE 2.1-4.2|IND")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


## USA
```{r}
v_regionall <- c("GCAM5.3_NGFS|USA", 
              "MESSAGEix-GLOBIOM 1.1|R11_NAM", 
              "REMIND-MAgPIE 2.1-4.2|USA")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```

# Scenario: Below 2°C
```{r}
u_scenario <- "Below 2°C"
```
## World
```{r}
v_region <- "World"
```

### Primary energy production
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_energysupply, u_models, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_electricutilities, u_models, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_liquidsplants, u_models, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_h2plants, u_models, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region == v_region, scenario == u_scenario), u_sectors_energydemand, u_models, SUM=u_sum_type)

```


## China
```{r}
v_regionall <- c("GCAM5.3_NGFS|China", 
              "MESSAGEix-GLOBIOM 1.1|R11_CPA", 
              "REMIND-MAgPIE 2.1-4.2|CHA")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


## EU
```{r}
v_regionall <- c("GCAM5.3_NGFS|EU-12", 
              "MESSAGEix-GLOBIOM 1.1|R11_WEU", 
              "REMIND-MAgPIE 2.1-4.2|EUR")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


## India
```{r}
v_regionall <- c("GCAM5.3_NGFS|India", 
              "MESSAGEix-GLOBIOM 1.1|R11_SAS", 
              "REMIND-MAgPIE 2.1-4.2|IND")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


## USA
```{r}
v_regionall <- c("GCAM5.3_NGFS|USA", 
              "MESSAGEix-GLOBIOM 1.1|R11_NAM", 
              "REMIND-MAgPIE 2.1-4.2|USA")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


# Scenario: Delayed transition
```{r}
u_scenario <- "Delayed transition"
```
## World
```{r}
v_region <- "World"
```

### Primary energy production
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_energysupply, u_models, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_electricutilities, u_models, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_liquidsplants, u_models, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_byModel_forReport(data_plot_diff_rel %>% filter(region == v_region, scenario == u_scenario), u_sectors_h2plants, u_models, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_world_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region == v_region, scenario == u_scenario), u_sectors_energydemand, u_models, SUM=u_sum_type)

```


## China
```{r}
v_regionall <- c("GCAM5.3_NGFS|China", 
              "MESSAGEix-GLOBIOM 1.1|R11_CPA", 
              "REMIND-MAgPIE 2.1-4.2|CHA")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


## EU
```{r}
v_regionall <- c("GCAM5.3_NGFS|EU-12", 
              "MESSAGEix-GLOBIOM 1.1|R11_WEU", 
              "REMIND-MAgPIE 2.1-4.2|EUR")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


## India
```{r}
v_regionall <- c("GCAM5.3_NGFS|India", 
              "MESSAGEix-GLOBIOM 1.1|R11_SAS", 
              "REMIND-MAgPIE 2.1-4.2|IND")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```


## USA
```{r}
v_regionall <- c("GCAM5.3_NGFS|USA", 
              "MESSAGEix-GLOBIOM 1.1|R11_NAM", 
              "REMIND-MAgPIE 2.1-4.2|USA")
```

### Primary energy supply
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energysupply, u_models, v_regionall, SUM=u_sum_type)
```

### Electric utilities
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_electricutilities, u_models, v_regionall, SUM=u_sum_type)
```

### Liquid fuels plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_liquidsplants, u_models, v_regionall, SUM=u_sum_type)
```

### Hydrogen plants
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_byModel_forReport(data_plot_diff_rel %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_h2plants, u_models, v_regionall, SUM=u_sum_type)
```

### Energy demand
```{r message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
draw_rfp_heatmap_region_diff_abs_byModel_forReport(data_plot_diff_abs %>% filter(region %in% v_regionall, scenario == u_scenario), u_sectors_energydemand, u_models, v_regionall, SUM=u_sum_type)

```